---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# caretForecast

<!-- badges: start -->

<!-- badges: end -->


The goal of caretForecast is to provide tools for forecasting time series data using various machine learning algorithms.

## Installation

The CRAN version with:

``` r
install.packages("caretForecast")

```


The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Akai01/caretForecast")
```
# Examples 

These are basic examples which shows you how to solve common problems with 
different ML models. 

## Examples of tidy forecasting via formula interface:

Load the packages:

```{r setup, message=FALSE}
library(caretForecast)
library(tsibble)
library(dplyr)
```

```{r tssible_data}
tourism_syd <- tourism %>%
  filter(Region == "Sydney")

tourism_syd %>%
  group_by(Purpose) %>%
  slice(1)
```


```{r plots}

tourism_syd %>%
  autoplot(Trips)

```


```{r fit, message=FALSE}

fit <- tourism_syd %>%
  model(
    caret = CARET(Trips ~ fourier(K = 2) + order(8) , caret_method = "lasso", verbose = FALSE)
  )
fit

```

```{r forecast}
fc <- fit %>%
  forecast(h = "5 years")
fc
```


```{r hilo}
fc %>%
  hilo(level = c(80, 95))
```


```{r plotfc, fig.height=10}
fc %>%
  autoplot(tourism_syd)
```




## Examples with ```ts``` objects:
### Note: User can train any caret supported regression model.




```{r example}
library(caretForecast)

# Forecasting with glmboost
data(retail_wide, package = "caretForecast")

i <- 8

dtlist <- caretForecast::split_ts(retail_wide[,i], test_size = 12)

training_data <- dtlist$train

testing_data <- dtlist$test

fit <- ARml(training_data, max_lag = 12, caret_method = "glmboost", 
            verbose = FALSE)

forecast(fit, h = length(testing_data), level = c(80,95), PI = TRUE)-> fc

accuracy(fc, testing_data)


autoplot(fc) + 
  autolayer(testing_data, series = "testing_data")



## NOTE : Promotions, holidays, and other external variables can be added in the model via xreg argument. Please look at the documentation of ARml.

# Forecasting with cubist regression

i <- 9

data(retail_wide, package = "caretForecast")

dtlist <- caretForecast::split_ts(retail_wide[,i], test_size = 12)

training_data <- dtlist$train

testing_data <- dtlist$test

fit <- ARml(training_data, max_lag = 12, caret_method = "cubist", 
            verbose = FALSE)

forecast(fit, h = length(testing_data), level = c(80,95), PI = TRUE)-> fc

accuracy(fc, testing_data)

autoplot(fc) + 
  autolayer(testing_data, series = "testing_data")



# Forecasting using Support Vector Machines with Linear Kernel

data(retail_wide, package = "caretForecast")

i <- 9

dtlist <- caretForecast::split_ts(retail_wide[,i], test_size = 12)

training_data <- dtlist$train

testing_data <- dtlist$test

fit <- ARml(training_data, max_lag = 12, caret_method = "svmLinear2", 
            verbose = FALSE, pre_process = c("scale", "center"))

forecast(fit, h = length(testing_data), level = c(80,95), PI = TRUE)-> fc

accuracy(fc, testing_data)

autoplot(fc) + 
  autolayer(testing_data, series = "testing_data")

get_var_imp(fc)

get_var_imp(fc, plot = F)



# Forecasting using Ridge Regression
data(retail_wide, package = "caretForecast")

i <- 8

dtlist <- caretForecast::split_ts(retail_wide[,i], test_size = 12)

training_data <- dtlist$train

testing_data <- dtlist$test

fit <- ARml(training_data, max_lag = 12, caret_method = "ridge", 
            verbose = FALSE)

forecast(fit, h = length(testing_data), level = c(80,95), PI = TRUE)-> fc

accuracy(fc, testing_data)

autoplot(fc) + 
  autolayer(testing_data, series = "testing_data")

get_var_imp(fc)

get_var_imp(fc, plot = F)
```


